Active Learning for SAT-Solver Benchmarking

### 2022-10-07 paper/paper.tex
abstract

\begin{abstract}
  Experimentation is one of the main phases in algorithm engineering, including the propositional-sat\-is\-fia\-bi\-li\-ty problem (SAT).
  While the field of SAT-solver benchmarking is well established, traditional bench\-mark-set-selection approaches do not optimize for benchmark runtime.
  Benchmark-set selection is the process of choosing a subset of instances out of a pool to be representative and reliable in discriminating SAT solvers.
  This paper presents an active-learning-based benchmark-set-selec\-tion approach that solves the \emph{New-Solver Problem}:
  Given a new solver, we want to find its ranking amidst its competitors with as little runtime as possible while still giving accurate ranking predictions.
  We can determine a new solver's rank regarding the SAT Competition 2022 Anniversary Track instances in about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset.
  We achieve this while still maintaining a prediction accuracy of about \SI{92}{\%} regarding the PAR-2 ranking of this solver if it were evaluated on the complete dataset.
  Additionally, we discuss the importance of instance families in the selection process. 
  Our tool provides the engineer of propositional-satisfiability solvers with a faster way of determining a new SAT-solver's performance in comparison to sampling the benchmark set by hand.

>>>>

\begin{abstract}
  Experimentation, in particular the evaluation of the runtime of a concrete implementation, is one of the most important phases in the development of algorithms.
  This also applies to solutions of the SAT problem (propositional sat\-is\-fia\-bi\-li\-ty).
  While the field of SAT solver benchmarking is well established, traditional benchmark selection approaches do not optimize for benchmark runtime.
  Benchmark compilation selects representative instances from a pool of instances such that they reliably discriminate SAT solvers based on their runtime.
  In this paper, we present an active learning based dynamic benchmark selection approach that predicts the rank of a new solver among its competitors with minimum running time and maximum rank prediction accuracy.
  We evaluated this approach using the Anniversary track dataset from the 2022 SAT Competition. 
  Our dynamic instance selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  In this paper, we also discuss the importance of instance families in the selection process. 
  Our tool provides a reliable way for SAT solver engineers to efficiently determine the performance of a new SAT solver.
